Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-02-27 abstract.tex
making progress with the introduction

% 
This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation. We evaluate the hazard considering over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, and for completeness, we also consider the partial contribution of the two remaining seismic zones, that is, Zagros to the south-west, and the central and eastern Iranian seismic zone. Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree in both the latitude and longitude directions. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events with magnitude greater than 3 within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Smoothing was done using a Gaussian filter in incremental intervals of magnitude. Seismicity parameters are calculated and smoothed for each region separately, and for comparison purposes, we also consider the combination of all the seismic zones as a uniform region. Seismic hazard curves are first obtained for two distinct models defined on two structural risk scenarios based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, and then combined into a single one to account for the proportion of reinforced and unreinforced structures. The results are presented in terms of expected peak ground acceleration curves and hazard maps and considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, and compared to equivalent estimations available in the literature at selected locations. Despite some localized differences \textcolor{red}{[???]}, we find our results to be in good agreement with previous results. Therefore, we find the method used here is appropriate to estimate seismic hazard for northern Iran. We conclude with an analysis of the results and its implications for the region, and highlight... or offer some additional thoughts about... \textcolor{red}{[Naeem: what would you say is the main conclusion or major finidng?]}.

>>>>

% 
This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data. We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh. For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zones. Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both the latitude and longitude directions. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Smoothing was done using a Gaussian filter in incremental intervals of magnitude. Seismicity parameters are calculated and smoothed for each region separately, and for comparison purposes, we also consider the combination of all the seismic zones as a uniform region. Seismic hazard curves obtained for two distinct models defined according to two structural risk scenarios. These scenarios are based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 for unreinforced and informal construction, and greater than 5.0 for modern structures following design regulations. We also present results for a combined scenario based on the proportion of reinforced and unreinforced structures. The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the difference observed due to the intrinsic differences in the methods employed here in light of results obtained by other previous studies. In conclusion, we find our results to be helpful in understanding seismic hazard for norther Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain a more robust estimates at specific areas of interest.

% -------------------------

% Naeem's comment about differences with previous studies...

% We may need to write the conclusion from other point of view. The method, attenuation relationship, and even data (some sort of) are different from other studies. So we expect to see different results. Not only we expect but at some point we should see some differences because of the method. There are some places that we don't have any recorded earthquake or they are not  as much to increase the hazard. In this study for those places we get lower hazard, but in studies based on recognizing faults as a source, they ends up with higher hazard. I think we can say that even though the other studies are good, but they are not complete and we need to use this method alongside them.

% Naeem's comment about GMPE...

% The attenuation relationship \citep{Kalkan2004} has been introduced in 2004 (Not recently). In 2014, \citet{Zafarani2014} evaluated many different attenuation relationship based on recently recorded data. They found \citet{Kalkan2004} has the best fit with data for PGA.

% Naeem's info about magnitude selection...

% We used earthquake with magnitude 3 and greater only after 2000, before that data are greater than 4.

% -------------------------

### 2016-02-27 introduction.tex
making progress with the introduction

>>>>

This article presents a new seismic hazard assessment for northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region. The Iranian plateau is located on the Himalayan-Alpine seismic belt. It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east. This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges \citep[e.g.,][]{Berberian_1981_Chap}. It also defines the seismic activity of the region, one with a long history of large magnitude ($M>7$) earthquakes dating back to the eight century, which has repeatedly damage Iran's infrastructure and taken the lives of thousands.

According to this tectonic setting and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the more elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}. Contemporary, well-accepted studies divide Iran into five major tectonic regions: Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran \citep[e.g.,][]{Mirzaei1998}. More recently, in a study aimed to develop a uniform earthquake catalog for Iran, \citet{Karimiparidari2013} further divided the Azerbaijan-Alborz region into two separate seismic zones: Azerbaijan and the Alborz Mountain Range, hereafter referred to simply as Alborz. We adopt the latter definition of six seismic basic seismic zones and focus our attention on those most relevant to the northern part of the country, that is, Azerbaijan, Alborz and Kopeh-Dagh.

Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}]. These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}}. While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk in high and therefore more complete and accurate assessments of seismic hazard are necessary.

We are particularly interested in the assessment of seismic hazard in northern Iran. This region has a significant population density with respect to the rest of the country, and includes some of its most populated cities: Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht. These cities alone house about 31.5 million people. They represent nearly 40 percent of the total population of Iran and a good portion of its economic activity. In this study we ...

In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
